### 2017-03-25 thesis/latex/thesis.tex
Thesis: partial commit of kb-kub testing.

\usepackage{tocbibind}
\usepackage{tocloft}
\usepackage{xpatch}

@@

\begin{document}
\newcommand{\listequationsname}{List of Equations}
\newlistof{myequations}{equ}{\listequationsname}
\newcommand{\myequations}[1]{%
\addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}

\xpretocmd{\listofmyequations}{\addcontentsline{toc}{chapter}{\listequationsname}}{}{}

\tableofcontents
\listoffigures
\clearpage
\listofmyequations
\newpage

@@

\begin{equation}
  \label{diffusion-equation}
  <x> = \sqrt{2Dt}
\end{equation}
\myequations{some equation}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l |}
    \hline
    T & [ATP] \\ \hline
    310.15 K & $1mM$\\ \hline
  \end{tabular}
  \caption{Physical constants of simulation.}{Table of physical constants used in simulation.}
  \label{table:parameter-table}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
    \hline
    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
  \end{tabular}
  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
  \label{table:parameter-table}
\end{figure}

%% \textit{Add in a plot of the binding rate fitting search}

\paragraph{Fitting rate constants by simulation}
\textit{Add in a plot of the binding rate fitting search}

>>>>

%% \usepackage{tocbibind}
%% \usepackage{tocloft}
\usepackage{xpatch}

@@

\begin{document}
%% \newcommand{\listequationsname}{List of Equations}
%% \newlistof{myequations}{equ}{\listequationsname}
%% \newcommand{\myequations}[1]{%
%% \addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}\par}

%% \xpretocmd{\listofmyequations}{\addcontentsline{toc}{chapter}{\listequationsname}}{}{}

%% \tableofcontents
\listoffigures
\clearpage
%% \listofmyequations
%% \newpage

@@

\begin{equation}
  \label{diffusion-equation}
  <x> = \sqrt{2Dt}
\end{equation}
%% \myequations{some equation}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l |}
    \hline
    T & [ATP] \\ \hline
    310.15 K & $1mM$\\ \hline
  \end{tabular}
  \caption{Physical constants of simulation.}{Table of physical constants used in simulation.}
  \label{table:simulation-std-conditions}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
    \hline
    Velocity & $\left<L_{step}\right>$ & $\tstep$ & $\tproc$ & $\tbb$ & $\tob$ \\ \hline
    134nm/s & 8nm & 0.06s & 7.9s & 0.0595s & 4.52e-4\\ \hline
  \end{tabular}
  \caption{Experimental values for fitting.}{Table calculating estimates for $\tbb$ and $\tob$.}
  \label{table:time-parameter-table}
\end{figure}

\paragraph{Fitting rate constants by simulation}
\textit{Add in a plot of the binding rate fitting search}\\

To find the ideal binding and unbinding rates of our model, we ran simulations at various $k_b$ and $k_{ub}$ conditions. The time each simulation spent in each state, $t_{bb}$ and $t_{ob}$, was compared with the experimental data shown in Table \ref{table:time-parameter-table}. Simulation behavior for a wide range of $k_b$ and $k_{ub}$ values is shown as a heat map in Figure \ref{fig:kb-kub-heatmap}.\\

\begin{figure}[h!]
  \centering
  \includegraphics[width=\textwidth]{../../plots/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
  \label{fig:kb-kub-heatmap}
\end{figure}
